### 2021-05-13 paper/fse21/intro.tex

At the same time, various JavaScript host environments require excessive
manual modeling of their behaviors for static analysis.  Because built-in functions and
host-dependent functions are implemented in native language like C and
C++ instead of JavaScript, their code is \textit{opaque} during static
analysis.  Thus, static analyzers often model their behaviors
manually, which is error-prone, tedious, and labor-intensive.
While several researchers have proposed automatic modeling
techniques~\cite{safewapi, model-ts}, since they utilize only type
information, they generate imprecise modeling compared with the manual approach.

@@

To alleviate these problems, researchers have leveraged
dynamic analysis during static analysis.  \inred{Because dynamic
analyzers such as Jalangi~\cite{jalangi} and DLint~\cite{dlint} run on
highly-optimized commercial JavaScript engines while static analyzers run on
their own interpreters, that leads to a great gap in performance.}
Figure~\ref{fig:performance} shows that the dynamic analyzer
Jalangi is 34.8x faster than the static analyzer SAFE for a subset of the
SunSpider benchmark \inred{that is input-independent and deterministic}.
Using high performance dynamic analysis, researchers have
reduced the scope of static analysis~\cite{determinacy, blendedJS} and constructed
initial abstract states~\cite{battles, eha} and automatic modeling of opaque
code~\cite{sra}.

@@

In this paper, we propose a novel technique to fully utilize
the high performance of dynamic analysis for JavaScript static
analysis in a sound manner by using \textit{dynamic shortcuts}.
During static analysis, one can take a dynamic shortcut, which
consists of three parts: 1) converting the current abstract state to
its corresponding \textit{{\sealed} state}, 2) performing
\textit{{\sealed} execution} on the {\sealed} state, and
3) converting the result of the {\sealed} execution to its
corresponding abstract state.  Our key observation is that we can use
the fast concrete execution for specific program parts while
preserving the soundness if they do not use abstract values.
For example, consider static analysis of the following code:
\begin{lstlisting}[style=myJSstyle,numbers=none]
    var v = ... // an abstract value
    var obj = { p1: v }, y = "p";
    x = obj[y + 1];
\end{lstlisting}
Because \jscode{y + 1} evaluates to \jscode{"p1"},
the third line assigns the abstract value of \jscode{v} stored in
\jscode{obj.p1} to the variable \jscode{x}.
Note that even though \jscode{obj} contains an abstract value \jscode{v},
because the third line does not ``use'' the value of \jscode{v},
we can concretely execute the code.  Based on this observation,
we introduce {\sealed} execution, which is concrete execution
using \textit{{\sealed} values}.  \inred{A {\sealed} value is a symbol
that represent an abstract value in {\sealed} execution}; it signals
the end of the current dynamic shortcut when the {\sealed}
execution tries to access its value.
To evaluate our technique, we implemented $\tool$ using both SAFE
and Jalangi and analyzed 269 official tests of Lodash 4 library.

>>>>

At the same time, JavaScript host environments require excessive
manual modeling of their behaviors for static analysis.  Because built-in functions and
host-dependent functions are implemented in native languages like C and
C++ instead of JavaScript, their code is \textit{opaque} during static
analysis.  Thus, static analyzers often model their behaviors
manually, which is error-prone, tedious, and labor-intensive.
While researchers have proposed automatic modeling
techniques~\cite{safewapi, model-ts}, since they utilize only type
information, they generate imprecise modeling compared with the manual approach.

@@

To alleviate these problems, researchers have leveraged
dynamic analysis during static analysis.  Unlike static analyzers that
run on their own interpreters, dynamic analyzers such as Jalangi~\cite{jalangi} and DLint~\cite{dlint}
run on highly-optimized commercial JavaScript engines, which makes them
much faster than static analyzers.
Figure~\ref{fig:performance} shows that the dynamic analyzer
Jalangi is 34.8x faster than the static analyzer SAFE for a subset of the
SunSpider benchmark that is input-independent and deterministic.
Using high performance dynamic analysis, researchers have
reduced the scope of static analysis~\cite{determinacy, blendedJS} and constructed
initial abstract states~\cite{battles, eha} and automatic modeling of opaque
code~\cite{sra}.

@@

In this paper, we propose a novel technique to fully utilize
the high performance of dynamic analysis for JavaScript static
analysis in a sound manner by using \textit{dynamic shortcuts}.
During static analysis, one can take a dynamic shortcut, which
consists of three parts: 1) converting the current abstract state to
its corresponding \textit{{\sealed} state}, 2) performing
\textit{{\sealed} execution} on the {\sealed} state, and
3) converting the result of the {\sealed} execution to its
corresponding abstract state.  Our key observation is that we can use
the fast concrete execution for specific program parts while
preserving the soundness if they do not use abstract values.
For example, consider static analysis of the following code:
\begin{lstlisting}[style=myJSstyle,numbers=none]
    var v = ... // an abstract value
    var obj = { p1: v }, y = "p";
    x = obj[y + 1];
\end{lstlisting}
Because \jscode{y + 1} evaluates to \jscode{"p1"},
the third line assigns the abstract value of \jscode{v} stored in
\jscode{obj.p1} to the variable \jscode{x}.
Note that even though \jscode{obj} contains an abstract value \jscode{v},
because the third line does not ``use'' the value of \jscode{v},
we can concretely execute the code.  Based on this observation,
we introduce {\sealed} execution, which is concrete execution
using \textit{{\sealed} values}.  A {\sealed} value is a symbol
that represent an abstract value in {\sealed} execution; it signals
the end of the current dynamic shortcut when the {\sealed}
execution tries to access its value.
To evaluate our technique, we implemented $\tool$ using SAFE
and Jalangi and analyzed 269 official tests of Lodash 4 library.

### 2021-05-13 paper/fse21/javascript.tex

We define the semantics of the view transition for the core language.  For abstract
memories, we use the notation $\absmem[L \mapstos \absval]$ to represent the
update of multiple abstract locations in $L$ with the abstract value $\absval$.
It performs the strong update if the abstract address for an abstract location
$(\absaddr, \_) \in L$ is singleton: $\abscount(\absaddr) = \absone$.
Otherwise, it performs the weak update for the analysis soundness.  We use
the increment function $\inc: \abscountset \times \absaddrset \rightarrow
\abscountset$ of the abstract counter defined as follows:
\[
  \inc(\abscount)(\absaddr_0) = \lambda \absaddr \in \absaddrset. \; \left\{
    \begin{array}{ll}
      \absone & \text{if} \; \absaddr = \absaddr_0 \wedge
      \abscount(\absaddr_0) = \abszero\\
      \absmany & \text{if} \; \absaddr = \absaddr_0 \wedge
      \abscount(\absaddr_0) = \absone\\
      \abscount(\absaddr) & \text{otherwise}
    \end{array}
  \right.
\]

@@

We define the {\sealed} states by not only extending the concrete values
$\valset$ with {\sealed} values $\symbset$ but also adding the abstract counters
$\abscountset$ as follows:
\[
  \begin{array}{r@{~}c@{~}l}
    \symbstset &=& \labset \times \memset \times \ctxtset \times \eaddrset
    \times \abscountset\\
    \ctxtset &=& \eaddrset \finmap ((\eaddrset \times \labset \times \locset)
    \uplus \symbset)\\
    \valset &=& \pvalset \uplus \oaddrset \uplus \fvalset \uplus \symbset\\
    \abscountset &=& \oaddrset \rightarrow \{ \abszero, \absone, \absmany \}\\
  \end{array}
\]
Because JavaScript provides open objects, the properties of objects can be dynamically added or deleted.
Moreover, since object properties are string values that can be constructed at run time,
it is difficult to perform sound strong updates in static analysis.
To check the possibility of strong updates during {\sealed} execution,
we augment its states with the abstract counters $\abscountset$.

For each abstract value in a given abstract state,
if the abstract value denotes a single concrete value,
the converter $\asconverter: (\viewset \times
\absdom) \rightarrow (\absimapset \times \symbstset)$
keeps it; otherwise, $\asconverter$ replaces the abstract
value with its unique identifier and maintains the mapping from the
unique identifier to the abstract value to construct an abstract instantiation map.
The opposite converter $\saconverter: (\absimapset \times
  \symbstset)  \rightarrow (\viewset \times \absdom)$
recovers abstract values from their unique identifiers using the abstract instantiation map.
We define the {\sealed} transition relation $\symbtrans$
only if the next step does not require actual values of any {\sealed} values.
Otherwise, a given {\sealed} state does not have any {\sealed}
transitions to apply.  For example, we add the following rule for the $\kwret$ statement:
\begin{mathpar}
  \inferrule
  {
    \prog(\lab) = \kwret \; \expr\\
    \exprrule{\symbst}{\expr}{\val}\\
    \ctxt(\addr) \in \symbset
  }
  {
    \symbst = (\lab, \mem, \ctxt, \addr, \abscount)\
    \symbtrans \excst
  }
\end{mathpar}
We extend each rule of the concrete semantics to support such behaviors of {\sealed} 
values.

>>>>

We define the semantics of the view transition for the core language.  For abstract
memories, we use the notation $\absmem[L \mapstos \absval]$ to represent the
update of multiple abstract locations in $L$ with the abstract value $\absval$.
It performs the strong update if the abstract address for an abstract location
$(\absaddr, \_) \in L$ is singleton: $\abscount(\absaddr) = \absone$.
Otherwise, it performs the weak update for the analysis soundness.  We use
the increment function $\inc: \abscountset \times \absaddrset \rightarrow
\abscountset$ of the abstract counter defined as follows:

\[
  \inc(\abscount)(\absaddr_0) = \lambda \absaddr \in \absaddrset. \; \left\{
    \begin{array}{ll}
      \absone & \text{if} \; \absaddr = \absaddr_0 \wedge
      \abscount(\absaddr_0) = \abszero\\
      \absmany & \text{if} \; \absaddr = \absaddr_0 \wedge
      \abscount(\absaddr_0) = \absone\\
      \abscount(\absaddr) & \text{otherwise}
    \end{array}
  \right.
\]

@@

We define {\sealed} states by not only extending the concrete values
$\valset$ with {\sealed} values $\symbset$ but also adding the abstract counters~
$\abscountset$:
% as follows:
\[
  \begin{array}{r@{~}c@{~}l}
    \symbstset &=& \labset \times \memset \times \ctxtset \times \eaddrset
    \times \abscountset\\
    \ctxtset &=& \eaddrset \finmap ((\eaddrset \times \labset \times \locset)
    \uplus \symbset)\\
    \valset &=& \pvalset \uplus \oaddrset \uplus \fvalset \uplus \symbset\\
    \abscountset &=& \oaddrset \rightarrow \{ \abszero, \absone, \absmany \}\\
  \end{array}
\]
Because JavaScript provides open objects, the properties of objects can be dynamically added or deleted.
Moreover, since object properties are string values that can be constructed at run time,
it is difficult to perform sound strong updates in static analysis.
To check the possibility of strong updates during {\sealed} execution,
we augment its states with the abstract counters $\abscountset$.

For each abstract value in a given abstract state,
if the abstract value denotes a single concrete value,
the converter $\asconverter: (\viewset \times
\absdom) \rightarrow (\absimapset \times \symbstset)$
keeps it; otherwise, $\asconverter$ replaces the abstract
value with its unique identifier and maintains the mapping from the
unique identifier to the abstract value to construct an abstract instantiation map.
The opposite converter $\saconverter: (\absimapset \times
  \symbstset)  \rightarrow (\viewset \times \absdom)$
recovers abstract values from their unique identifiers using the abstract instantiation map.
We define the {\sealed} transition relation $\symbtrans$
only if the next step does not require actual values of any {\sealed} values.
Otherwise, a given {\sealed} state does not have any {\sealed}
transitions to apply.  For example, we add the following rule:
\begin{mathpar}
  \inferrule
  {
    \prog(\lab) = \kwret \; \expr\\
    \exprrule{\symbst}{\expr}{\val}\\
    \ctxt(\addr) \in \symbset
  }
  {
    \symbst = (\lab, \mem, \ctxt, \addr, \abscount)\
    \symbtrans \excst
  }
\end{mathpar}
for the $\kwret$ statement. We extend each rule of the concrete semantics
to support such behaviors of {\sealed} values.

### 2021-05-13 paper/fse21/motivation.tex

\begin{figure}[t]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle]
function concat() {
  var length = arguments.length;
  if (!length) return [];
  var array = arguments[0],
      args  = Array(length - 1),
      index = length;
  while (index--)
    args[index-1] = arguments[index];
  return arrayPush(isArray(array) ?
    copyArray(array) : [array],
    baseFlatten(args, 1));
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Lodash's \jscode{concat} function}
    \label{fig:concat}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=13]
function changeCountry(G) { ...
  if (G.selectedVal === "US" && state) {
    // deterministic arguments of `concat`
    state.items = _.concat([["Other", "Other"]],
      WebinarBase.questions.state.items);
    state.selectedVal = _.head(_.head(C.items));
  }
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Call of \jscode{concat} with concrete values}
    \label{fig:changeCountry}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=22]
function getData(e) {
  var option = ... // option for server connection
  post(option).then(function(e) {
    if (e.total_records && e.total_records > 0) {
      // non-deterministic arguments of `concat`
      this.pastEvents =
        _.concat(this.pastEvents, e.events);
      this.total = e.total_records;
    } else this.noPastData = !0
  })
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Call of \jscode{concat} with abstract values}
    \label{fig:getData}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Lodash library function and its uses in \code{zoom.us}}
  \label{fig:example}
  \vspace*{-1em}
\end{figure}

In this section, we explain the motivation of dynamic shortcuts
using real-world examples shown in Figure~\ref{fig:example}.
We first describe their behaviors and then explain how we can utilize
dynamic shortcuts during their static analysis.

@@

Figure~\ref{fig:example}(b) and Figure~\ref{fig:example}(c) show use
cases of the \jscode{concat} function in the \code{zoom.us}~\cite{zoom} site.
It is the homepage of Zoom, which is a videotelephony software program developed by Zoom
Video Communications and it is ranked as the 15th popular web site according
to Alexa\footnote{https://www.alexa.com/siteinfo/zoom.us} in February 2021.

\paragraph{Dynamic shortcuts with concrete values.}
When a function is called with concrete values, we can perform
dynamic analysis instead of static analysis.
For example, \jscode{changeCountry} in Figure~\ref{fig:example}(b)
is invoked when a user selects a country from a drop-down list in the registration page.
It calls the \jscode{concat} function to update the drop-down list of
states or provinces on lines 16--17.  However, when the user selects ``United States of America,''
which is \jscode{"US"}, two arguments are pre-defined with
deterministic values; the first one is an array literal
\jscode{[["Other", "Other"]]} and the second one is an array of pairs
of abbreviations and names of the states defined as follows:
\begin{lstlisting}[style=myJSstyle,numbers=none]
WebinarBase.questions.state.items =
  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
\end{lstlisting}
Moreover, \jscode{this} also has a concrete value, the Lodash top-level object \jscode{\_}.
Thus, we can perform dynamic analysis by invoking \jscode{concat} with
\jscode{\_} as its \jscode{this} value and the above concrete values as arguments. 
By skipping the analysis of the function call on lines 17--18 and
utilizing the result of dynamic analysis, it improved the analysis performance.

>>>>

\begin{figure}[t]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle]
function concat() {
  var length = arguments.length;
  if (!length) return [];
  var array = arguments[0],
      args  = Array(length - 1),
      index = length;
  while (index--)
    args[index-1] = arguments[index];
  return arrayPush(isArray(array) ?
    copyArray(array) : [array],
    baseFlatten(args, 1));
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Lodash's \jscode{concat} function}
    \label{fig:concat}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=13]
function changeCountry(G) { ...
  if (G.selectedVal === "US" && state) {
    // deterministic arguments of `concat`
    state.items = _.concat([["Other", "Other"]],
      WebinarBase.questions.state.items);
    state.selectedVal = _.head(_.head(C.items));
  }
}
    \end{lstlisting}
    \vspace*{-1.5em}
    \caption{Call of \jscode{concat} with concrete values}
    \label{fig:changeCountry}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=22]
function getData(e) {
  var option = ... // option for server connection
  post(option).then(function(e) {
    if (e.total_records && e.total_records > 0) {
      // non-deterministic arguments of `concat`
      this.pastEvents =
        _.concat(this.pastEvents, e.events);
      this.total = e.total_records;
    } else this.noPastData = !0
  })
}
    \end{lstlisting}
    \vspace*{-1.5em}
    \caption{Call of \jscode{concat} with abstract values}
    \label{fig:getData}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Lodash library function and its uses in \code{zoom.us}}
  \label{fig:example}
  \vspace*{-1.5em}
\end{figure}

This section explains the motivation of dynamic shortcuts
using real-world examples in Figure~\ref{fig:example}.
We describe their behaviors and explain how we can utilize
dynamic shortcuts during static analysis.

@@

Figure~\ref{fig:example}(b) and Figure~\ref{fig:example}(c) show use
cases of the \jscode{concat} function in the \code{zoom.us}~\cite{zoom} site.
It is the homepage of Zoom, a videotelephony software by Zoom
Video Communications and it is ranked as the 15th popular web site according
to Alexa\footnote{https://www.alexa.com/siteinfo/zoom.us} in February 2021.

\paragraph{Dynamic shortcuts with concrete values.}
When a function is called with concrete values, we can perform
dynamic analysis instead of static analysis.
For example, \jscode{changeCountry} in Figure~\ref{fig:example}(b)
is invoked when a user selects a country from a drop-down list in the registration page.
It calls the \jscode{concat} function to update the drop-down list of
states or provinces on lines 16--17.  However, when the user selects ``United States of America,''
which is \jscode{"US"}, two arguments are pre-defined with
deterministic values; the first one is an array literal
\jscode{[["Other", "Other"]]} and the second one is an array of pairs
of abbreviations and names of the states defined as follows: \\[-.5em]
\begin{lstlisting}[style=myJSstyle,numbers=none]
WebinarBase.questions.state.items =
  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
\end{lstlisting}
\noindent\smallskip
Moreover, \jscode{this} also has a concrete value, the Lodash top-level object~\jscode{\_}.
Thus, we can perform dynamic analysis by invoking \jscode{concat} with~\jscode{\_}
as its \jscode{this} value and the above concrete values as arguments. 
By skipping the analysis of the function call on lines 17--18 and
utilizing the result of dynamic analysis, it improved the analysis performance.
